---
title: "Lab 01 - Hello R"
author: "Lindsey Wilson"
date: "1/17/23"
output: 
  html_document: 
    fig_width: 12
    fig_height: 12
    theme: journal
    highlight: tango
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

According to the help file, the dataset has 1846 rows and 3 variables ("dataset", "x", and "y")

```{r}
vars <- names(datasaurus_dozen)
vars
```

### Exercise 2

The correlation between "x" and "y" in the dino_data dataset is -0.0645.

And here's what the data look like plotted:

```{r plot-dino, fig.height=5, fig.width=5}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And here's the code I used (was given) to find the correlation

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Below we have the code that allows us to plot the star data

First, we create a dataset with just the star data

Then, we plot that data using the same code we used for the dino data

```{r plot-star, fig.height=5, fig.width=5}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(star_data, aes(x = x, y = y)) + 
  geom_point()
```

The same code from Ex. 2 also lets us find the correlation between "x" and "y"

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

So we can see that the correlation comes out to -0.0630. That's almost exactly the same as in the dino data!

### Exercise 4

Following the example of the last few sections, we can find the correlation between "x" and "y" in the circle data

```{r cor-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

circle_data %>%
  summarize(r = cor(x, y))
```

And plot it

```{r plot-circle, fig.height=5, fig.width=5}
ggplot(circle_data, aes(x = x, y = y)) +
  geom_point()
```

So one again, even though the shape of the data is very different from Ex. 2 & 3, the correlation is almost exactly the same.

### Exercise 5

The code below lets us visualize all of the datasets at once

```{r all-plots}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

They look really different! However, we can see below that, in spite of that, the correlation between "x" and "y" across the datasets doesn't vary much

```{r all-cor}
all_correlations <- datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y))
all_correlations
```
