---
title: "Lab 01 - Hello R"
author: "Lindsey Wilson"
date: "1/17/23"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

According to the help file, the dataset has 1846 rows and 3 variables ("dataset", "x", and "y")

```
?datasaurus_dozen
```

### Exercise 2

The correlation between "x" and "y" in the dino_data dataset is -0.0645.

And here's what the data look like plotted:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And here's the code I used (was given) to find the correlation!

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Add code and narrative as needed.
Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient.
To finish, clean up the narrative by removing these instructions.



```{r plot-star}

```

I'm some filler text, you should replace me with more meaningful text...

```{r cor-star}

```

### Exercise 4

Add code and narrative as needed.
Note that two R chunks are given but they are not labeled.
Use the convention from above to name them appropriately.

```{r}

```

```{r}

```

### Exercise 5

Add code and narrative as needed.

To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.




